Advantages of mixed quantum channels for information processing

### 2019-02-26 decorrelation/mixed_unitaries.tex
filling in some of the sections that needed filling in

%-------------Header begins here----------------------------------------
\begin{document}
\title{Advantages of mixed unitary operators for quantum information processing}

@@

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.

@@

Quantitative bounds on the performance of quantum circuits can be constructed using the diamond distance []. \note{Discuss subadditivity of diamond norm here... The resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates. While these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict. The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors. For long circuits, this can add up extremely quickly. 
}. 
Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs. Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{simple_example.pdf}
  \caption{An example of a mixed unitary process. Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$). Each time the gate is used, one of these implementations is chosen at random. The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
  \label{fig:simple_example}
\end{figure}

@@

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mathematical preliminaries}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma)/2^n,
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.  The action of a gate is then given by the usual matrix multiplication:
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
\end{equation}
Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:

@@

\note{this should go somewhere:}
There are often many possible ways of implementing any given target quantum gate. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011}

@@

\note{fix this} A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.  The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$. From this definition, we can use linearity to compute the AGI of a MUP. We see that the AGI of any MUP will be the convex sum of the consituent fidelities, with the same weighting. The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MUP than any of the processes being mixed.

Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel. Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed. The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits. However, it is not the only optimization target that can be chosen.

@@

The error operator corresponding to a rotation error by angle $\epsilon$ is then:
\begin{equation}
\error(\epsilon) =
	\left(\begin{array}{ccccc}
		1 & 0 & 0 & 0 \\ 
		0 & \cos\epsilon & \sin\epsilon  & 0  \\
		0 & -\sin\epsilon & \cos\epsilon & 0  \\
		0 & 0 & 0 & 1
	\end{array} 	
	\right)
\end{equation}
\note{Don't be dumb with right hand rules}
The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\epsilon)}_\diamond \simeq \epsilon$, while the fidelity of the channel is $\mathcal{F}(\error(\epsilon)) = \epsilon^2$. If we were construct two channels, one with error $\error(\epsilon)$ and one with error $\error(-\epsilon)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\epsilon) + \error(\epsilon)\right)$. The effective channel then has a matrix representation:
\begin{equation}
	\error(\epsilon) =
	\left(\begin{array}{ccccc}
		1 & 0 & 0 & 0 \\ 
		0 & \cos\epsilon & 0  & 0  \\
		0 & 0 & \cos\epsilon & 0  \\
		0 & 0 & 0 & 1
	\end{array} 	
	\right) \simeq \mathcal{I} - 
	\left(\begin{array}{ccccc}
		0 & 0 & 0 & 0 \\ 
		0 & \epsilon^2/2 & 0  & 0  \\
		0 & 0 & \epsilon^2/2 & 0  \\
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
And with same average process fidelity, $\epsilon^2$, but now a suppressed diamond norm $\epsilon^2$. Now write this in terms of the error generators $\error(\epsilon) = \exp(\epsilon G)$ where
\begin{equation}
	G =
	\left(\begin{array}{ccccc}
		0 & 0 & 0 & 0 \\ 
		0 & 0 & 1  & 0  \\
		0 & -1 & 0 & 0  \\
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
The effective generator vanishes at first order.

@@

Alternatively, \note{Draw box around the (2,4),(2,3),(3,4) elements of the G matrix}. We can then eliminate off diagonal entries, resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable. \note{more here about alternative method. Also discuss Fig 2.}.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no 0MUPs. b) The origin is contained in the covex hull after adding an additional control solution. Because there are more than $n+1$ implementations, there exist an infinite number of 0MUPs. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a 0MUP may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a 1MUP.}
  \label{fig:vectorspace}
\end{figure}

@@

\subsection{First-order generators} % (fold)
\label{sub:first_order_generators}
\note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
If our primary goal is for our MUP to have increased performance, then a useful target for constructing MUPs is instead minimizing the diamond norm. As in Section \ref{sec:simple_example}, the MUP that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$. Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$. While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application. However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MUP with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MUP with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MUP with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MUP is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. This forms a convex optimization problem, and can be written as:

@@

%Another interesting property of the MUP given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift. In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways. Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$. In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order. Given these considerations from this simple example, we will now consider a numerical strategy for generating MUPs.

@@

\subsection{Adding robustness} % (fold)
\label{sub:adding_robustness}
\note{this section is a little bit heavy on the notation - is there anything we can do to ease that? Perhaps in the introduction we can specify the problem a little more clearly and then this can be just a restriction of that general model }
While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MUP will degrade. Thus, we would like to design MUPs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}. Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed unitary process is robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MUP}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MUP satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MUP as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MUP will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MUP} as:
\begin{equation}\label{eq:MUP-relaxed}
\begin{gathered}
\sum\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP. Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.

To generate robustly mixed unitary processes, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
\begin{equation}
{\bold{D}^{\ell}} =  \left(\begin{array}{cccc}
		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		D^\ell_{m_{11}} &  &  D^\ell_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}

@@

\begin{equation}\label{eq:minimization_l2}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation}
with $\eta \geq 0$. By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor. The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$. Naively generating the 1Q 0MUP in the previous section results in nontrivial support on all the members of the control family. However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MUP uses just five of the controls. This shows that through adding constraints to our optimization routine, we can make the MUP practically useful.

@@

\subsection{Sparsity Constraints}
As a practical consideration, we would also like to regularize our objective function to enforce sparsity. Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls. As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}. In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. Thus we would prefer that our solution, if we are forming a $0$MUP, ignores $H_4$. However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'. Thus we would like to be frugal in which controls we select. In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:

>>>>

%-------------Header begins here----------------------------------------
\begin{document}
\title{Advantages of mixed quantum channels for information processing}

@@

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016, 1901.08035}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.

@@

Quantitative bounds on the performance of quantum circuits can be constructed using the diamond distance, $||\cdot||_\diamond$. This particular metric, defined in Section \ref{sec:representing_quantum_gates}, has the appealing property of being subadditive, namely for a channels $\mathcal{F}_1$, $\mathcal{F}_2$ we have:
\begin{equation}
||\mathcal{F}_1\circ\mathcal{F}_2||_\diamond \leq ||\mathcal{F}_1||_\diamond + ||\mathcal{F}_2||_\diamond
\end{equation}
The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors. For long circuits, this can add up extremely quickly, and while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict. Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs. Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates. In this case, the resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{simple_example.pdf}
  \caption{An example of a mixed quantum channel. Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$). Each time the gate is used, one of these implementations is chosen at random. The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
  \label{fig:simple_example}
\end{figure}

@@

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mixed quantum channels}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma)/2^n,
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. For a single qubit, this is $\vec\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}$.  The action of a gate is then given by the usual matrix multiplication:
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
\end{equation}
Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:

@@

@@

A \textit{mixed quantum channel} (MQC) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.  The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$. From this definition, we can use linearity to compute the AGI of a MQC. We see that the AGI of any MQC will be the convex sum of the consituent fidelities, with the same weighting. The diamond norm, however, is non-linear function of the channel, and can in general be smaller for a MQC than any of the processes being mixed.

When performing a quantum gate, there are often many possible ways of it might be implemented. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} Following this, Campbell considered the important problem of minimizing the diamond norm of the resulting error channel. Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed. The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits. However, it is not the only optimization target that can be chosen.

@@

The error operator corresponding to a rotation error by angle $\epsilon$ is then:
\begin{equation}
\error(\epsilon) =
	\left(\begin{array}{ccccc}
		1 & 0 & 0 & 0 \\ 
		0 & \cos\epsilon & \sin\epsilon  & 0  \\
		0 & -\sin\epsilon & \cos\epsilon & 0  \\
		0 & 0 & 0 & 1
	\end{array} 	
	\right)
\end{equation}

The associated diamond distance of this channel is $\abs{\mathcal{I} - \error(\epsilon)}_\diamond \simeq \epsilon$, while the fidelity of the channel is $\mathcal{F}(\error(\epsilon)) = \epsilon^2$. If we were construct two channels, one with error $\error(\epsilon)$ and one with error $\error(-\epsilon)$, then we could construct a new channel with error $\error_{\rm eff} = \frac{1}{2}\left(\error(\epsilon) + \error(\epsilon)\right)$. The effective channel then has a matrix representation:
\begin{equation}
	\error(\epsilon) =
	\left(\begin{array}{ccccc}
		1 & 0 & 0 & 0 \\ 
		0 & \cos\epsilon & 0  & 0  \\
		0 & 0 & \cos\epsilon & 0  \\
		0 & 0 & 0 & 1
	\end{array} 	
	\right) \simeq \mathcal{I} - 
	\left(\begin{array}{ccccc}
		0 & 0 & 0 & 0 \\ 
		0 & \epsilon^2/2 & 0  & 0  \\
		0 & 0 & \epsilon^2/2 & 0  \\
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
And with same average process fidelity, $\epsilon^2$, but now a suppressed diamond norm $\epsilon^2$. Now write this in terms of the error generators $\error(\epsilon) = \exp(\epsilon G)$ where
\begin{equation}
	G =
	\left(\begin{array}{ccccc}
		0 & 0 & 0 & 0 \\ 
		0 & 0 & -1  & 0  \\
		0 & 1 & 0 & 0  \\
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}

The effective generator vanishes at first order.

@@

Alternatively, we might consider eliminating off-diagonal entries of G:
\begin{equation}
	\left(\begin{array}{@{}ccccc@{}}
		0 & 0 & 0 & 0 \\ 
  		\cline{3-4}
    	0 & 0 & \multicolumn{1}{|c}{-1} & \multicolumn{1}{c|}{0} \\
    	\cline{3-3}		
		0 & 1 & 0 & \multicolumn{1}{|c|}{0}\\
		\cline{4-4}	
		0 & 0 & 0 & 0
	\end{array} 	
	\right)
\end{equation}
 resulting in a matrix that is guaranteed to be Pauli stochastic, and thus somewhat easily simulable problem. In the case of a single qubit, it is clear that our generator is expressible as $\hat{n}\cdot\vec{\Sigma}$, where $\vec{\Sigma}$ is again the vector of Pauli operators. The condition that the off-diagonal terms vanish is then again the same condition that the origin lies in the convex hull of the vectors $\vec{n}_i$ for each $G_i$.
 \note{more here about alternative method. Also discuss Fig 2.}.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no 0MQCs. b) The origin is contained in the covex hull after adding an additional control solution. Because there are more than $n+1$ implementations, there exist an infinite number of 0MQCs. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a 0MQC may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a 1MQC.}
  \label{fig:vectorspace}
\end{figure}

@@

\subsection{First-order generators} % (fold)
\label{sub:first_order_generators}
\note{say that we are linearizing the diamond distance calculation -  rewrite this whole thing}
If our primary goal is for our MQC to have increased performance, then a useful target for constructing MQCs is instead minimizing the diamond norm. As in Section \ref{sec:simple_example}, the MQC that minimizes the diamond norm has matrix elements given by:
\begin{equation}\label{eq:balanced}
\mathcal{M}_{jk} = \frac{1}{2}\tr(\sigma_j^{\dagger}U_{-\epsilon}\sigma_kU_{-\epsilon}^{\dagger}) + \frac{1}{2}\tr(\sigma_j^{\dagger}U_{\epsilon}\sigma_kU_{\epsilon}^{\dagger})
\end{equation}
This channel will have a diamond norm proportional to $\epsilon^2$, whereas any other combination will have a linear dependence on $\epsilon$. Contrast this with the fact that any linear combination of $\{U_{\epsilon}, U_{-\epsilon}\}$ minimizes the AGI of the resulting channel with a value of $\epsilon^2$. While selecting the convex mixture of unitaries that minimizes the AGI is  trivial, the problem of efficiently minimizing the diamond norm can be difficult, and may be the relevant quantity to consider depending on the application. However, as discussed in \cite{Campbell2017}, a sufficient condition to minimize the diamond norm of a MQC with error generators $\{H_j\}$ to first order is:
\begin{equation}\label{eq:campbell-condition}
\sum \omega_j H_j = 0
\end{equation}
In \cite{Campbell2017} Campbell constructs an algorithm that, given an oracle to approximate unitaries, finds a MQC with this property. Alternatively one might ask the question: \textit{Given a collection of controls, how can I produce a MQC with minimal diamond norm?} Such a situation may arise if there is a natural family of controls that implement a desired gate, or if, as we consider later (Section \ref{sec:numerical_results}), we simply randomly generate a collection of gate implementations. In these situations, one can equivantly use convex optimization to solve this problem. Consider the matrix whose rows are the vectorized Hamiltonians at our disposal, i.e. for $m$, $n\times n$ Hamiltonians:
\begin{equation}\label{eq:vectorized_hamiltonians}
	\bold{H} = \left(\begin{array}{cccc}
		H_{1_{11}} & H_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		H_{m_{11}} &  &  H_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}
If our weighting vector for our MQC is $\omega$, we can rewrite this sum as a matrix product whose two-norm will be zero if and only if the sum is zero. Additionally, this optimization needs to be constrained so that $\omega$ only contains positive values that sum to one. This forms a convex optimization problem, and can be written as:

@@

%Another interesting property of the MQC given in Equation \ref{eq:balanced} is that it maintains its first-order insensitivity even in the presence of drift. In particular, if the control amplitudes that implement these gates drift, they will drift in equal and opposite ways. Thus, the resulting depolarizing channel (see Figure \ref{fig:simple_example}) will have a time-dependent strength, but it will remain first-order insensitivity to the static detuning $\epsilon$. In Section \ref{sec:robustly_mixed} we will provide a method for producing controls that exhibit this robustness to drift to arbitrary order. Given these considerations from this simple example, we will now consider a numerical strategy for generating MQCs.

@@

\subsection{Adding robustness} % (fold)
\label{sub:adding_robustness}
\note{this section is a little bit heavy on the notation - is there anything we can do to ease that? Perhaps in the introduction we can specify the problem a little more clearly and then this can be just a restriction of that general model }
While mixed quantum channels offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MQC will degrade. Thus, we would like to design MQCs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in Equation \ref{eq:campbell-condition}. Instead of only requiring that the $0^{th}$ derivative averages to zero, we will impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
If the dimension of $\vec{\delta}$ is $d$, the indices $i_0, \ldots, i_n$ take on values in $1, \ldots, d$ and this matrix has $d^n$ entries. 
We say that a mixed quantum channel is robust to order $\ell$ (an $\ell$MQC) if for all $1 \leq k \leq \ell$:
\begin{equation}\label{eq:MQC}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^n = \vec{0}\\
\end{gathered}
\end{equation}
In particular, we see that a 0MQC satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MQC is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MQC as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MQC will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can find controls such that $|D_j^n|\approx\epsilon$, we can approximate Equation \ref{eq:MQC} as:
\begin{equation}\label{eq:MQC-relaxed}
\begin{gathered}
\sum\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell showed that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MQC. Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MQC.

To generate robustly mixed quantum channels, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to Equation \ref{eq:vectorized_hamiltonians}:
\begin{equation}
{\bold{D}^{\ell}} =  \left(\begin{array}{cccc}
		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		D^\ell_{m_{11}} &  &  D^\ell_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}

@@

\begin{equation}\label{eq:minimization_l2}
\begin{split}
&\underset{n\in[N]}{\textbf{minimize}}\{\\
&\ \ \bunderbrace{\textbf{minimize}: }{\omega_j\geq0, |\omega|_1=1} ||{\bold{D}^{\ell}}^T\omega||+ \eta\sum\omega_j||D^0_j||_2\\
&\ \ \textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=0\\
&\}
\end{split}
\end{equation}
with $\eta \geq 0$. By making $\eta$ larger, we can supress the diamond norm to second order, while ensuring that we are selecting those that will give us a smaller prefactor. The absolute value of $\eta$ depends on the particular numerical values in $\bold{D}^\ell$. Naively generating the 1Q 0MQC in the previous section results in nontrivial support on all the members of the control family. However, by rewriting the minimization to impose this sparsity constraint discussed in Section \ref{sec:robustly_mixed}, the resulting 0MQC uses just five of the controls. This shows that through adding constraints to our optimization routine, we can make the MQC practically useful.

@@

\subsection{Sparsity Constraints}
As a practical consideration, we would also like to regularize our objective function to enforce sparsity. Control electronics often have a limited amount of waveform memory, and thus it is important that MQCs have non-trivial probability support on a small number of controls. As an example of where this would be necessary is given in Figure \ref{fig:vectorspace}. In b), it is clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. Thus we would prefer that our solution, if we are forming a $0$MQC, ignores $H_4$. However, if we additionally want our controls to form a 1MQC, we see from Subfigure D that we need $H_4$ in our control set, in which case we would like our algorithm to exclude $H_1$, since its derivative is contained in the convex hull of the others'. Thus we would like to be frugal in which controls we select. In many machine learning contexts, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity in solutions, however this is insufficient in this context as we already constrain the one norm of $\omega$ to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:
